Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-30 ms.tex
abstract

\begin{abstract}
  We calculate steady-state, one-dimensional hydrodynamic profiles of
  hot gas in slowly accreting (``quiescent") galactic nuclei for a
  range of central black hole masses $M_{\bullet}$, parameterized gas
  heating rates, and observationally-motivated stellar density
  profiles.  Mass is supplied to the circumnuclear medium by stellar
  winds, while energy is injected primarily by stellar winds,
  supernovae, and black hole feedback.  Analytic estimates are derived
  for the stagnation radius (where the radial velocity of the gas
  passes through zero) and the black hole accretion rate, $\dot{M}$,
  as a function of $M_{\bullet}$ and the gas heating efficiency, the
  latter being related to the star-formation history.  We assess the
  conditions under which radiative instabilities develop in the hydrostatic region near the stagnation radius, both in the
  case of a single burst of star formation and for the average star
  formation history predicted by cosmological simulations.  By
  combining a sample of measured nuclear X-ray luminosities, $L_{X}$,
  of nearby quiescent galactic nuclei with our results for
  $\dot{M}(M_{\bullet})$ we address whether the nuclei are consistent with
  accreting in a steady-state, thermally-stable manner for radiative
  efficiencies predicted for radiatively inefficiency accretion flows.  However, thermally-stable
  accretion cannot explain the short average growth times of low mass
  black holes in the local universe, which must instead result from
  gas being fed in from large radii, due either to gas inflows or
  thermal instabilities acting on larger, galactic scales.  Our
  results have implications for attempts to constrain the occupation
  fraction of SMBHs in low mass galaxies using the mean $L_{\rm
    X}-M_{\bullet}$ correlation, as well as the predicted diversity of
  the circumnuclear densities encountered by relativistic outflows
  from tidal disruption events.
\end{abstract}

>>>>

\begin{abstract}
  We calculate steady-state, one-dimensional hydrodynamic profiles of
  hot gas in slowly accreting (``quiescent") galactic nuclei for a
  range of central black hole masses $M_{\bullet}$, parameterized gas
  heating rates, and observationally-motivated stellar density
  profiles.  Mass is supplied to the circumnuclear medium by stellar
  winds, while energy is injected primarily by stellar winds,
  supernovae, and black hole feedback.  Analytic estimates are derived
  for the stagnation radius (where the radial velocity of the gas
  passes through zero) and the black hole accretion rate, $\dot{M}$,
  as a function of $M_{\bullet}$ and the gas heating efficiency, the
  latter being related to the star-formation history.  We assess the
  conditions under which radiative instabilities develop in the
  hydrostatic region near the stagnation radius, both in the case of a
  single burst of star formation and for the average star formation
  history predicted by cosmological simulations.  By combining a
  sample of measured nuclear X-ray luminosities, $L_{X}$, of nearby
  quiescent galactic nuclei with our results for
  $\dot{M}(M_{\bullet})$ we address whether the nuclei are consistent
  with accreting in a steady-state, thermally-stable manner for
  radiative efficiencies predicted for radiatively inefficiency
  accretion flows.  We find thermally-stable accretion cannot explain
  the short average growth times of low mass black holes in the local
  universe, which must instead result from gas being fed in from large
  radii, due either to gas inflows or thermal instabilities acting on
  larger, galactic scales.  Our results have implications for attempts
  to constrain the occupation fraction of SMBHs in low mass galaxies
  using the mean $L_{\rm X}-M_{\bullet}$ correlation, as well as the
  predicted diversity of the circumnuclear densities encountered by
  relativistic outflows from tidal disruption events.
\end{abstract}
